Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2018-02-13 QPQ9/Submit/response.txt

Dear referee,

We thank you very much for careful reading of our manuscript, and your comments and criticism.

@@

>After carefully reviewing the manuscript, I found multiple significant issues with the study, and consequently it does
>not currently meet the standards for publication. These issues must be addressed before the paper can be accepted, and
>I request the opportunity to review the paper again after the authors have made revisions with the hope that it can be
>accepted for publication. The main issues are summarized below and more detailed discussion follows.
>
>1) The conclusions of the paper rely heavily on accurate quasar redshift measurements because redshift errors will
>influence both the centroid and dispersion measured in the stacked background absorption spectra. Indeed, the measured
>centroids and velocity dispersions in the stacked absorption spectra are comparable with expected quasar redshift
>biases and scatter. In an attempt to address this issue, the authors adopt redshift bias measurements from the
>literature, but the bias measurements used are not appropriate for the redshift measurement techniques that are
>described in the previous QPQ papers (details to follow). Significant additional work is required to demonstrate that
>the offset in the observed absorption centroid is real and not due to redshift measurement errors.

We thank you for pointing out the importance of accurate redshift measurements. We have addressed the
suggested additional work in the details to follow.

@@

We have added text to explain how redshifts are measured. We acknowledge the confusion in calling the line-centering
algorithm a centroiding method. Our algorithm calculates the mode of a line given by (3*median - 2*mean), applied to
the upper 60% of the emission line. Shen+16 states that difference between the peak and the centroid is not
significant, except for the broad line Hbeta, which we did not use in redshift measurements. We have further obtained
individual measurements of centroids and peaks in Shen+16 thru private communication. There is essentially no
difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s
difference for MgII on average. We may expect the difference between a mode and a peak is even smaller.

In the first version of the submitted manuscript, there are two redshift measurement techniques in the z ~ 2 sample:
our custom line-centering algorithm, and the algorithm of Hewett&Wild10. We thank you for scrutinizing the
redshift measurement techniques, which helps strengthen our results. In this re-submitted manuscript, for all z > 1.6
sample we measure redshifts of all quasars using our own custom line-centering algorithm instead of adopting values
from Hewett&Wild10. After we purge the quasars whose redshift measurement is dominated by CIII], we find that on
average there is essentially no difference between the Hewett&Wild10 redshifts and our own measured redshifts.
Furthermore, Shen+16 has stated throughout the paper that their work is consistent with Hewett&Wild10 on redshift
estimates based on MgII emission and on the average systemic bias. Therefore, for the z ~ 1 sample, where either the
[OIII] or the MgII emission has good data quality, and where we do not measure an intriguing asymmetry in the average
absorption, we continue to adopt the Hewett&Wild10 redshifts.

@@

As explained above, we have sufficient number of absorbing components that they should tend toward a Gaussian
distribution in the stack. We are able to model the stack by a Gaussian multiplied to a pseudocontinuum. Our visual
inspection does not hint at a broader component in the stack. QPQ7 reported the redshift of the strongest Lya
absorption within the search window. The QPQ7 sample has spectra of all resolutions. It requires echellette or
echelle resolution to identify the metal-associated absorbers. In QPQ8, a scatter plot of the optical depth weighted
centroid of the absorption systems is shown. In the Appendix of QPQ8, the absorption profiles of the individual
components are shown. We have counted 6 of them are at negative velocities, while 15 of them are at positive
velocities. text have been added to reflect these numbers.

>Major point 3:
>
>The authors do not provide enough detail regarding the fit to the mean stack. In particular, for MgII and CIV two
>gaussian with fixed doublet separation and width are fit to the stack. However, no details on the doublet ratio range
>allowed are given. This is particularly important for CIV where the doublets are not well resolved in the stack.
>Consequently, the velocity centroid and doublet ratio will be degenerate and uncertainty due to this degeneracy must
>be addressed.

We thank you for pointing out the insufficient detail in the text. The doublet ratio is allowed to vary
between 2:1 to 1:1.

@@

In QPQ8, we have estimated the random incidence of optically thick absorbers. Text has been added to reflect
these numbers. As our Monte Carlo simulations demonstrate, outflows are not required to reproduce the observed
amplitude and dispersion of the mean absorption.

>Major point 5:
>
>Several papers in the literature that are cited are mis-represented in the introduction. In particular:
>
>Johnson et al. 2015 is cited as concluding that the large velocity of absorbing gas observed around quasars is due to
>outflows. This is not the case. The paper considers several possible explanations including large-scale structure,
>galaxy interactions, and outflows. The conclusion of the paper is that none of these possibilities can satisfactorily
>explain the observed properties of cool gas around quasars.
>
>Gauthier et al. 2013, Muzahid 2015, and Zahedy et al. 2016 exhibit velocity spreads of ~600, 300-400, and 600 km/s
>respectively, which is comparable with those observed in the QPQ survey, contrary to the claim in the paper. This
>inaccurate statement needs to be clarified and corrected.
>
>These misrepresentations combined with the fact that the paper applies redshift bias corrections from the literature
>that are not appropriate for their redshift measurement techniques indicates that the authors need to carefully review
>the paper and ensure that the citations to the literature are correctly represented and applied.

We thank you for clarifying the explanation to Johnson+15's results. We have updated the text to reflect that
outflows is only one possibility. Gauthier+13 is a single sightline, and the velocity width Dv90 of the MgII
absorber is less than the average of QPQ8 CII absorber. Muzahid+15 found an absorber with Dv90 less than 555 km/s in
OVI and NV, and still smaller for other ions. Zahedy+16's sample has average Dv90 smaller than that of QPQ8.

### 2018-02-27 QPQ9/Submit/qpq9_resubmit_3.tex
response to third referee report

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational
motion and Hubble flow, and galactic-scale outflows are not required to explain the large
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift.
The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems. We show that the observed offsets may be produced
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the
gas is not flowing into the galaxy.
\end{abstract}

@@

Direct observations of galactic flows are difficult to acquire. Detecting the presence of
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are
accentuated for distant, young galaxies, where flows of gas are predicted to prevail
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions,
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we
measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the
circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic
redshift. The offsets, $\delta v$, are often positive, with the sign convention that positive
velocities indicate a redshift from the systemic. From a sample of 7 \ion{C}{2} systems and 10
\ion{C}{4} systems, we measured the velocity interval that encompasses 90\% of the total optical
depth, $\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is
$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for
\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed
all previous measurements from galaxies and/or absorption systems at any epoch.

@@

Furthermore, we include only those spectra with average signal-to-noise ratio (S/N) exceeding 5.5
per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths
of the metal ion transitions. This criterion is a compromise between maximizing sample size versus
maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame
\AA \ is necessary for properly estimating the continuum, as well as identifying mini-broad
absorption line systems associated to the background quasar, which will significantly depress the
flux level. We also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$
around a considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$
bands. The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA
\ respectively.

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin,
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue.
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is
included in the modeling. The absorptions frequently exhibit large velocity widths. The blue dashed
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The
$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are
$25\,{\rm km\,s^{-1}}$ and $27\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling
errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments,
continuum placement errors, and redshift errors. The individual spectra of background quasars are
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to
a common spectral resolution.
The individual spectra are then combined with a mean or a median
statistic.
{\bf Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.}
Bad pixels in the individual spectra have been masked before generating the
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather
than scatter in the flux of individual observations. The mean statistic of the individual spectra
yields a good estimate of the average absorption and preserves equivalent width. The median
statistic is less sensitive to {\bf outliers. However, the median opacity at any velocity channel is
rather small, since the discrete absorbers are spread throughout the entire velocity window.
A pixel is not affected unless there are more than 50\% of quasar pairs with absorption at its
velocity.} The analysis on the median velocity field is thus subject to larger uncertainty. In the
following we present stacked spectra using both the mean and the median statistic.

@@

{\bf Visually, there are two absorption components. One component is the uniform depression in the
continuum level in the stack resulting from absorbers unassociated with the foreground
quasars. The other component comes from absorbers associated with the foreground quasars and
distribute around their systemic velocities. To model the absorption, we introduce
a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.}
We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
to the data, we measure the centroid of the \ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$ and
the $1\sigma$ dispersion to be $293\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with
smaller offset and a more uncertain dispersion.

{\bf To test whether the dispersion in the average absorption associated with the foreground quasars is
well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
window surrounding the absorption centroid, while fitting a continuum to the rest of the
$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
One may also speculate on the existence of a broader absorption component hidden in the depressed
continuum. We try replacing the constant absorption component with a broad Gaussian component in our
modeling. We find that this second Gaussian component has essentially the same amplitude as the initial
constant absorption component, and is wider than the entire velocity window for stacking.
This weak and very broad component has no effect on the centroid and width of the narrow,
associated Gaussian component. We therefore consider that one single Gaussian component is a good
description of the average absorption associated with the foreground quasars.
Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
the foreground quasars, and hence will not affect the average absorption measured for the foreground
quasars. Their contribution to the average absorption should result in a tilt in the
pseudo-continuum, which is insignificant.}

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has a centroid at
$+235\,{\rm km\,s^{-1}}$, and a dispersion of $330\,{\rm km\,s^{-1}}$, consistent with the full
sample.

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
allow the doublet ratio to vary from 2:1 to 1:1.
{\bf The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
pronounced for \ion{C}{4}, although we find that a double ratio closer to 2:1 better captures the
absorption at the central few pixels. We state that the modeling of the doublets is presented for
consistency check, but the analysis focuses on \ion{C}{2}.}
The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

@@

To assess the statistical significance of the measured velocity offsets, we perform a boostrap analysis
by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile
to model each bootstrap realization, and quote the standard deviation in the bootstrap
realizations to be the scatter in the centroids of the data. The scatters
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
absorption.

{\bf One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2*}\,1334, absorption from \ion{C}{2*}\,1335
would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334. Among these nine subsystems, only one,
labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
Hence, contamination from \ion{C}{2*}\,1335 is insignificant and could not be responsible for the
observed redshift in the centroid.}

@@

Since the large scatter in the centroids represents intrinsic variation rather than redshift
errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we
consider that the asymmetry signal in the $z\sim2$ sample is likely to be real. In the Discussion
section, we discuss two possible explanations for the asymmetry.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black. In thick, green, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, shifted to the centroid of the stack of the data, and broadened
by the mean redshift error in the data. The model is a good description of the data, with a
dispersion within modeling error of the dispersion in the data. We overplot in dashed, yellow an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dashed, magenta an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observation.
}
\label{fig:monte}
\end{figure}

>>>>

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}.
{\bf We find that the mean absorptions exhibit large velocity widths
$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems.
We find the observed widths are consistent with gas in gravitational
motion and Hubble flow. However, while the observation of large widths alone does not require
galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
is anisotropic or intermittent.}
\end{abstract}

@@

Direct observations of galactic flows are difficult to acquire. Detecting the presence of
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are
accentuated for distant, young galaxies, where flows of gas are predicted to prevail
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions,
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we
measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the
circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic
redshift.
{\bf From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
systems, we measured the velocity interval that encompasses 90\% of the total optical depth,
$\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is
$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for
\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed
all previous measurements from galaxies and/or absorption systems at any epoch.
The offsets, $\delta v$, are often positive, with the sign convention that positive
velocities indicate a redshift from the systemic.
}

@@

Furthermore, we include only those spectra with average signal-to-noise ratio (S/N) exceeding 5.5
per rest-frame \AA\ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths
of the metal ion transitions. This criterion is a compromise between maximizing sample size versus
maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame
\AA\ is necessary for properly estimating the continuum, as well as identifying mini-broad
absorption line systems associated to the background quasar, which will significantly depress the
flux level. We also require that the region of the spectrum that is $\pm3000\,{\rm km\,s^{-1}}$
around a considered metal ion transition does not overlap with strong atmospheric ${\rm O}_2$
bands. The ${\rm O}_2$ A- and B-band span 7595\textendash7680\,\AA \ and 6868\textendash6926\,\AA
\ respectively.

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin,
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue.
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is
included in the modeling. The absorptions frequently exhibit large velocity widths. The blue dashed
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The
$1\sigma$ modeling error for the
{\bf dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
$25\,{\rm km\,s^{-1}}$ respectively, which are}
also the typical modeling errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments,
continuum placement errors, and redshift errors. The individual spectra of background quasars are
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to
a common spectral resolution.
The individual spectra are then combined with a mean or a median
statistic.
Spectra with broad absorption-line systems and mini-broad absorption-line systems are excluded.
Bad pixels in the individual spectra have been masked before generating the
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather
than scatter in the flux of individual observations. The mean statistic of the individual spectra
yields a good estimate of the average absorption and preserves equivalent width. The median
statistic is less sensitive to outliers. However, the median opacity at any velocity channel is
rather small, since the discrete absorbers are spread throughout the entire velocity window.
A pixel is not affected unless there are more than 50\% of quasar pairs with absorption at its
velocity. The analysis on the median velocity field is thus subject to larger uncertainty. In the
following we present stacked spectra using both the mean and the median statistic.

@@

Visually, there are two absorption components. One component is the uniform depression in the
continuum level in the stack resulting from absorbers unassociated with the foreground
quasars. The other component comes from absorbers associated with the foreground quasars and
distribute around their systemic velocities. To model the absorption, we introduce
a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.
We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
to the data, we measure
{\bf the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
\ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$. The dispersion suggests extreme kinematics, while
the centroid suggests an asymmetry that contradicts the standard expectation.}
The median
stack, on the other hand, shows weaker absorption,
{\bf and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.}

To test whether the dispersion in the average absorption associated with the foreground quasars is
well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
window surrounding the absorption centroid, while fitting a continuum to the rest of the
$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
One may also speculate on the existence of a broader absorption component hidden in the depressed
continuum. We try replacing the constant absorption component with a broad Gaussian component in our
modeling. We find that this second Gaussian component has
{\bf an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider}
than the entire velocity window for stacking.
This weak and very broad component has no effect on the {\bf width and the centroid} of the narrow,
associated Gaussian component. We therefore consider that one single Gaussian component is a good
description of the average absorption associated with the foreground quasars.
Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
the foreground quasars, and hence will not affect the average absorption measured for the foreground
quasars. Their contribution to the average absorption should result in a tilt in the
pseudo-continuum, which is insignificant.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has
{\bf a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$},
consistent with the full sample.

To model the mean and median absorption of \ion{C}{4}\,1548 and \ion{Mg}{2}\,1796, we introduce a
second Gaussian with separation equal to the doublet separation ($498\,{\rm km\,s^{-1}}$ and
$769\,{\rm km\,s^{-1}}$ respectively), and tie the dispersion of the two lines in a doublet. We
allow the doublet ratio to vary from 2:1 to 1:1.
The centroid is degenerate with the doublet ratio in our modeling. This degeneracy is more
pronounced for \ion{C}{4}, although we find that a double ratio closer to 2:1 better captures the
absorption at the central few pixels. We state that the modeling of the doublets is presented for
consistency check, but the analysis focuses on \ion{C}{2}.
The modeling results show that the velocity fields
of \ion{C}{4} and \ion{Mg}{2} are consistent with \ion{C}{2}, i.e.\ large dispersion and centroid
is skewed toward positive velocities.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
{\bf We overplot in dashed, yellow an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dot dashed, yellow an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observed width.
In thick, gold, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, and broadened
by the mean redshift error in the data. While this model has a dispersion within modeling error of the
dispersion in the data. the centroid of the stack of the data appears to be redshifted
from the systemic. A model with only gravitational motions and Hubble flows cannot explain
this putative asymmetry.}
}
\label{fig:monte}
\end{figure}

{\bf To assess the statistical significance of the observed dispersion, we perform a bootstrap
analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption
profile to model each bootstrap realization. We find that} a width of
$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter in
the bootstrap realizations
(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.

In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian
absorption model of the Monte Carlo simulations.
{\bf In the figure, the Gaussian absorption model is
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.}
The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$,
about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
stack of the sub-sample with [\ion{O}{3}] redshifts as well.
{\bf One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
velocities that are typical for quasar-mass halos, and adopt a different $\sigma_{\rm rms}$ accordingly.
The best-studied coeval, more typical star-forming
galaxies are the Lyman-break galaxies. Their clustering strength implies a characteristic halo
mass of $M_{\rm halo}\approx10^{11.6}\,M/{\rm M_\odot}$ \citep{Bielby+13,Malkan+17}, corresponding to
$\sigma_{\rm rms}=114\,{\rm km\,s^{-1}}$.
If we adopt this smaller $\sigma_{\rm rms}$ insead,for absorbers outside the loosely
defined quasar CGM boundary, at $\gtrsim300$\,kpc, the stack of mock spectra will have a $1\sigma$
dispersion of $247\,{\rm km\,s^{-1}}$. This is again within modeling errors of the observed intrinsic
dispersion.}
We also test for the
sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering
analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$
sightline may in fact intercept more than one optically thick absorber. We double the number of
absorbers for each mock sightline, and find the measured dispersion only increases by several
${\rm km\,s^{-1}}$. Thus, before the putative asymmetry is confirmed, the hypothesis that the
observed velocity width is only produced by a
combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical
processes are not necessary to explain the large velocity fields.

Although we acknowledge the possibility that our Gaussian model does not capture all the powers
at extreme velocities, we also caution that occasional large kinematic offsets do not make a strong
case against gravitational motions. Firstly, quasars occasionally inhabit extremely overdense environments
such as protoclusters \citep[e.g.,][]{Hennawi+15}. Secondly, the probability of intercepting a random,
unassociated absorber is boosted by large-scale clustering. Hence occasional extreme velocities would not
necessitate outflows. Our preferred kinematic measure is thus the dispersion in the average absorption.

@@

{\bf We quote} the standard deviation in the bootstrap
realizations to be the scatter in the centroids of the data. The scatters
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
absorption.

One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2}\,1334, absorption from \ion{C}{2*}\,1335
would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334.
{\bf Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.}
Among these nine subsystems, only one,
labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
{\bf We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
$\approx+40\,{\rm km\,s^{-1}}$.}
Hence, contamination from \ion{C}{2*}\,1335 could not be responsible for the observed redshift in
the centroid.

@@

Since the large scatter in the centroids represents intrinsic variation rather than redshift
errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we consider
that
{\bf systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.}
%the asymmetry signal in the $z\sim2$ sample is likely to be real.
In the Discussion section, we discuss two possible explanations for the asymmetry.

@@
